Reanalysis Step 1: Data Preparation

### 2025-08-14 reanalysis-1-data_preparation.qmd
fix bug

# Assess missing data for analysis variables
missing_summary <- df_analysis |>
  select(all_of(c(ps_model_vars, "outcome_va_vi_binary"))) |>
  summarise(across(everything(), ~ sum(is.na(.)))) |>
  pivot_longer(everything(), names_to = "variable", values_to = "n_missing") |>
  mutate(
    pct_missing = round(n_missing / nrow(df_analysis) * 100, 2),
    var_type = case_when(
      variable %in% c("outcome_va_vi_binary") ~ "Outcome",
      variable == "ever_lapse_binary" ~ "Exposure",
      TRUE ~ "Covariate"
    )
  ) |>
  arrange(desc(n_missing))

@@

# Create summary table
df_analysis |>
  select(all_of(summary_vars)) |>
  summary()

>>>>

# Assess missing data for analysis variables
missing_summary <- df_analysis |>
  dplyr::select(dplyr::all_of(c(ps_model_vars, "outcome_va_vi_binary"))) |>
  dplyr::summarise(dplyr::across(everything(), ~ sum(is.na(.)))) |>
  tidyr::pivot_longer(everything(), names_to = "variable", values_to = "n_missing") |>
  dplyr::mutate(
    pct_missing = round(n_missing / nrow(df_analysis) * 100, 2),
    var_type = dplyr::case_when(
      variable %in% c("outcome_va_vi_binary") ~ "Outcome",
      variable == "ever_lapse_binary" ~ "Exposure",
      TRUE ~ "Covariate"
    )
  ) |>
  dplyr::arrange(desc(n_missing))

@@

# Create summary table
df_analysis |>
  dplyr::select(dplyr::all_of(summary_vars)) |>
  summary()
